\pkg{cleanR}: Your Personal Maid for Cleaning Datasets in \proglang{R}

### 2016-10-16 latex/article.Rnw
Man pages + TeX

@@

In \pkg{cleanR} the clean function

<<>>=
library(cleanR)
data(testData)
head(testData)
@

<<>>=
                                        # clean(testData)
2+3
@

% \includepdf[fitpaper=true, pages=-]{test.pdf}

>>>>

\newcommand{\hl}[1]{\textcolor{magenta}{#1}}
\newcommand{\R}{\proglang{R}}

@@

In \pkg{cleanR} the clean function is the primary workhorse and it
should be an ideal starting place

First we
<<>>=
library(cleanR)
data(diamonds)
head(diamonds)
data(testData)
#head(testData)
@

To produce summary data-cleaning document

<<>>=
clean(testData, replace=TRUE, openResult=FALSE)
@

By default, a ... is produced and the result is shown in
Figure~\ref{fig:example1}.

\begin{figure}[!htp]
\begin{center}
\includegraphics[page=2]{cleanR_testData.pdf}
%\includepdf[pages={2}, pagecommand={}]{cleanR_testData.pdf}
\end{center}
\label{fig:example1}
\caption{Example output from running XXXX on the testData
  dataset. First a summary of the full dataset, }
\end{figure}

### 2016-10-16 latex/article.tex
Man pages + TeX

In \pkg{cleanR} the clean function

\begin{Schunk}
\begin{Sinput}
> library(cleanR)
> data(testData)
> head(testData)
\end{Sinput}
\begin{Soutput}
  charVar factorVar numVar intVar boolVar keyVar emptyVar _joeVar jack__var
1       a         a      1      1    TRUE      1        1       1         1
2       b         b      2      2   FALSE      2        1       2         2
3       c         c      3      3    TRUE      3        1       3         3
4       a         a      4      4    TRUE      4        1       4         4
5       b         b      5      5    TRUE      5        1       5         5
6       d         d      6      6   FALSE      6        1       6         6
  numOutlierVar smartNumVar      cprVar   cprKeyVar miscodedMissingVar
1             1           0 010101-1111 010101-1111                  .
2             2           0 020102-2929 020102-2929                   
3             3           0 121201-1902 121201-1902                nan
4             4           0 030729-2222 030729-2222                NaN
5             5           0 080909-1212 080909-1212                NAN
6             6           0 010101-1111 020202-0101                 na
\end{Soutput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
>                                         # clean(testData)
> 2+3
\end{Sinput}
\begin{Soutput}
[1] 5
\end{Soutput}
\end{Schunk}

% \includepdf[fitpaper=true, pages=-]{test.pdf}

>>>>

In \pkg{cleanR} the clean function is the primary workhorse and it
should be an ideal starting place

First we
\begin{Schunk}
\begin{Sinput}
> library(cleanR)
> data(diamonds)
> head(diamonds)
\end{Sinput}
\begin{Soutput}
  carat       cut color clarity depth table price    x    y    z
1  0.23     Ideal     E     SI2  61.5    55   326 3.95 3.98 2.43
2  0.21   Premium     E     SI1  59.8    61   326 3.89 3.84 2.31
3  0.23      Good     E     VS1  56.9    65   327 4.05 4.07 2.31
4  0.29   Premium     I     VS2  62.4    58   334 4.20 4.23 2.63
5  0.31      Good     J     SI2  63.3    58   335 4.34 4.35 2.75
6  0.24 Very Good     J    VVS2  62.8    57   336 3.94 3.96 2.48
\end{Soutput}
\begin{Sinput}
> data(testData)
> #head(testData)
\end{Sinput}
\end{Schunk}

To produce summary data-cleaning document

\begin{Schunk}
\begin{Sinput}
> clean(testData, replace=TRUE, openResult=FALSE)
\end{Sinput}
\end{Schunk}

By default, a ... is produced and the result is shown in
Figure~\ref{fig:example1}.

\begin{figure}[!htp]
\begin{center}
\includegraphics[page=2]{cleanR_testData.pdf}
%\includepdf[pages={2}, pagecommand={}]{cleanR_testData.pdf}
\end{center}
\label{fig:example1}
\caption{Example output from running XXXX on the testData
  dataset. First a summary of the full dataset, }
\end{figure}
